---
title: "MUTEX Twelve-month-olds disambiguate new words using mutual exclusivity"
author: Basia Pomiechowska
output: html_document
---

`data/dataindividual` contains individual participants' data. 

Note that different eye trackers were used acress experiments (E1: TOBII TX 300, E2: TOBII T60XL), resulting in different sampling frequencies (E1: 120 Hz; E2: 60 Hz). For plotting purposes, the data from Experiment 1 where downsampled by a factor of 2.

Each data file has the following structure:

$id$ - unique ID identifying each participant

$condition$ - highlighting condition (experimental v. control)

$word$ - word heard at test (familiar v. novel)

$trial$ - unique trial ID within each labeling condition (1 to 4)

$phase$ - test phase (baseline v. test)

$timesample$ - sample number within each phase

$aoifam$ - aoi hits recorded in the familiar object AOI

$aoiunfam$ - aoi hits recorded in the unfamiliar object AOI

Libraries and set up.

```{r message=FALSE, warning=FALSE, , paged.print=FALSE, include=FALSE}
library(readxl)
library(tidyverse)
library(ggpubr)
library(rstatix)
```

Read in individual data from data/participants.
```{r include=FALSE}
# Set the path
setwd("~/Documents/GitHub/mutex/data/dataindividual/")

#Get file names of individual data files
my_files <- list.files(pattern = "xlsx$")

#Loop through participants; add individual data sets to the summary data frame
results <- data.frame()
for (i in 1:length(my_files)) {
  print(my_files[i])
  aux <- read_excel(my_files[i])
  results <- rbind(results,aux)
}

rm(aux)

results$phase <- factor(results$phase)
results$condition <- factor(results$condition, levels = c("experimental", "control"),
                            labels = c("Experimental", "Control"))
```

Add experiment and order.
```{r}
results <- results %>%
  mutate(exp = ifelse(id < 21,"Experiment 1", "Experiment 2")) %>%
  mutate(order = ifelse((id <= 10 | (id >= 21 & id <= 30)), "Experimental first", "Experimental second"))
```

Compute time course of plftest.
```{r}
results$timeplf <- results$aoifam/(results$aoifam+results$aoiunfam)
```

# Average

Derive PLF at test.

```{r}
auxmean <- results %>%
  group_by(exp, order, id, condition, word, phase, trial, trialid) %>%
  summarize(sumfam = sum(aoifam, na.rm = TRUE), 
            sumdist = sum(aoiunfam, na.rm = TRUE),
            .groups = "keep") %>%
  mutate(plf = sumfam/(sumfam+sumdist)) %>%
  mutate(totalhits = sumfam+sumdist) #new
```

Corrplf.

```{r}
corrplf <- auxmean %>%
  select(exp, order, id, condition, word, phase, trial, trialid, plf) %>%
  pivot_wider(names_from = "phase", 
                    values_from = c("plf"), 
                    values_fn = unique) %>%
  mutate(corrplf = test-baseline)
```

Save the summary data.
```{r}
library(openxlsx)
write.xlsx(corrplf, "data/data_test.xlsx", sheetName = "data")
```

# Baseline correction

merge(resultsall, randomize, by=c("expOrder","trialNumber"))

```{r}
aux <- corrplf %>% 
  ungroup(exp,order,id,condition, word, trial) %>%
  select(id, trialid, baseline, test, corrplf)

results <- merge(results, aux, by = c("id","trialid")) 

results <- results %>%
  mutate(timecorrplf = timeplf - baseline)
```

#Figures

```{r}
#ret
auxplotindividual <- results %>%
  filter(phase == "test") %>%
  group_by(id, condition, word, timesample) %>%
  summarize(meancorrplf = mean(timecorrplf, na.rm = TRUE), .groups = "keep")

auxplot <- results %>%
  filter(phase == "test") %>%
  group_by(exp, condition, word, timesample) %>%
  get_summary_stats(timecorrplf, type = "mean_se")
  #summarize(meancorrplf = mean(timecorrplf, na.rm = TRUE), .groups = "keep")
```

Moving average.
```{r}
library(pracma)
auxplot$meanmove <- movavg(auxplot$mean, 7, type = "s")
```

```{r}
library(ggsci)
aux <- auxplot #%>% filter(condition == "Experimental")
  
a <- ggplot(data=aux, aes(x=timesample, y=meanmove, color=word)) +
  theme_light() +
          theme(
            plot.title = element_text(size = 16),
            plot.subtitle = element_text(size = 10),
            strip.text = element_text(size = 10),
                panel.grid.major.y = element_blank(),
                panel.grid.minor.y = element_blank(),
                panel.grid.major.x = element_blank(),
                panel.grid.minor.x = element_blank(),
                legend.position="bottom",
                axis.text=element_text(size=10),
                axis.title.y=element_text(size=14,face="bold"),
                #axis.title.x = element_blank(),
                #axis.text.x = element_blank(),
                axis.ticks.x = element_blank()) +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 90, size = .25, linetype = "dashed") +
  geom_vline(xintercept = 210, size = .25, linetype = "dashed") +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean - se, 
                      ymax = mean + se, 
                      fill = word), alpha = 0.2, colour = NA) +
  scale_y_continuous(name="corrPLF", limits=c(-.45, .45), breaks = c(-.4,-.2,0,.2,.4)) +
  scale_x_continuous(name= "Time (seconds)", breaks = c(1, 60, 120, 180, 240, 300), labels = c("0", "1", "2", "3", "4", "5")) +
  facet_grid(condition ~ exp, switch = "y") +
  scale_color_npg() +
  scale_fill_npg() +
  theme(
    strip.background = element_rect(fill="white"),
    strip.text = element_text(size=12, 
                              color="black", margin = margin(.25,.15,.25,.15, "cm")),
    strip.placement = "outside") +
  ggtitle(label = "Experiments 1-2")

#, subtitle = "Data collapsed across block orders"

a
```

```{r}
auxc2 <- results %>%
  filter(phase == "test" & condition == "Control" & exp == "Experiment 2") %>%
  group_by(exp, order, condition, word, timesample) %>%
  get_summary_stats(timecorrplf, type = "mean_se")

auxc2$meanmove <- movavg(auxc2$mean, 7, type = "s")
```


```{r}
auxc2$order <- factor(auxc2$order, 
                    levels = c("Experimental second", "Experimental first"),
                    labels = c("Control in block 1","Control in block 2"))
```


```{r}
library(ggsci)

b <- ggplot(data=auxc2, aes(x=timesample, y=meanmove, color=word)) +
  theme_light() +
          theme(
            plot.title = element_text(size=16),
            plot.subtitle = element_text(size = 10),
            strip.text = element_text(size = 14),
                panel.grid.major.y = element_blank(),
                panel.grid.minor.y = element_blank(),
                panel.grid.major.x = element_blank(),
                panel.grid.minor.x = element_blank(),
                legend.position="bottom",
                axis.text=element_text(size=10),
                axis.title.y=element_text(size=14,face="bold"),
                axis.ticks.x = element_blank()) +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 90, size = .25, linetype = "dashed") +
  geom_vline(xintercept = 210, size = .25, linetype = "dashed") +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean - se, 
                      ymax = mean + se, 
                      fill = word), alpha = 0.2, colour = NA) +
  scale_y_continuous(name="corrPLF", limits=c(-.4, .6)) +
  scale_x_continuous(name= "Time (seconds)", breaks = c(1, 60, 120, 180, 240, 300), labels = c("0", "1", "2", "3", "4", "5")) +
  facet_wrap(. ~ order) +
  scale_color_npg() +
  scale_fill_npg() +
  theme(
    strip.background = element_rect(fill="white"),
    strip.text = element_text(size=12, 
                              color="black", margin = margin(.15,.15,.15,.15, "cm"))) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 25, b = 0, l = 0))) +
  ggtitle(label = "Experiment 2", subtitle = "Control condition data split by block order")

b
```

```{r}
fig <- ggarrange(a,NULL,b, nrow = 3, heights = c(1,.05, .75))
  
setwd("~/Documents/GitHub/mutex/plots/")

ggsave("figure5.png", plot = last_plot(), width = 16, height = 20, units = c("cm"))
```


