---
title: "Twelve-month-olds disambiguate new words using mutual exclusivity"
author: Basia Pomiechowska
output:
  html_document:
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
---

# Load packages and data

Load packages.
```{r message=FALSE, warning=FALSE, , paged.print=FALSE, include=FALSE}
library(readxl)
library(tidyverse)
library(ggpubr)
library(rstatix)

library(plyr)
library(emmeans) 
library(afex)
library(sjstats)
```

Load data.

```{r include=FALSE}
dataHighlighting <- read_excel("data/data_PLF_highlighting.xlsx",sheet="PLF")
```

# Data structure

data_PLF_highlighting.xlsx contains:

* $Experiment$         -- Experiment 1, Experiment 2

* $ID$                 -- unique ID identifying each 
participant

* $Experimental_ H$     -- average PLF during highlighting in the 
experimental conditions

* $Control_ H$          -- average PLF during highlighting in the control conditions

* $Order$              -- order of block presentation (experimental condition first v. experimental condition second)



data_PLF_highlighting.xlsx contains:

* `Experiment` -- Experiment 1, Experiment 2

* `ID` -- unique ID identifying each participant

* `Experimental_H`-- average PLF during highlighting in the 
experimental conditions

* `Control_H` -- average PLF during highlighting in the control conditions

* `Order` -- order of block presentation (experimental condition first v. experimental condition second)

# Experiment 1

## Supplementary analysis

This analysis looks at the proportion of looking at the familiar object (PLF) during highlighting.

Gather data into long format.

```{r include=FALSE}
#Gather the columns into long format
e1_highlighting <- dataHighlighting %>%
  filter(Experiment == "Experiment 1") 
```

```{r include=FALSE}
e1_highlighting_long <- e1_highlighting %>%
  gather(key="Condition", value="PLF_H", c("Experimental_H","Control_H"))

#Convert Time as factor
e1_highlighting_long$Condition <- factor(e1_highlighting_long$Condition,
                  levels = c("Experimental_H","Control_H"),
                  labels = c("Experimental","Control"))
```


#### Descriptive statistics
Compute the summary descriptive statistics.
```{r echo=FALSE}
e1_highlighting_long %>%
  group_by(Condition) %>%
  get_summary_stats(PLF_H,type = "mean_sd")
```

#### Normality

Perform the Shapiro-Wilk test of normality with word x condition x order.

```{r echo=FALSE}
#Normality
e1_highlighting_long %>%
  group_by(Condition) %>%
  shapiro_test(PLF_H)
```

#### Comparison btwn highlighting conditions

This comparison was carried using a paired-samples t test.

```{r echo=FALSE}
t.test(e1_highlighting$Control_H, e1_highlighting$Experimental_H, paired = TRUE)
```

```{r}
cohensD(e1_highlighting$Control_H, e1_highlighting$Experimental_H, method = "paired")
```

#### Figure

```{r echo=FALSE}

m <- stat_summary(geom ="point", fun.y=mean, shape=18, size=4, color="blue", fill="blue", 
                  position = position_dodge(width = 0.75)) 

h1 <- ggplot(data = e1_highlighting_long, aes(x=Condition, y=PLF_H)) +
  theme_light() +
  geom_boxplot(outlier.size = -1, fill = "gray95", size = .25, width = .4) +
  geom_jitter(color="gray50",position = position_jitter(.1), size = 1.55) +
  theme(strip.text = element_text(size = 16),
        plot.title = element_text(size = 24),        
        panel.grid.minor.y = element_blank(),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.x =element_text(size=20),
                axis.text.y =element_text(size=20),
                axis.title.y=element_blank(),
                axis.title.x = element_blank()) +
  geom_hline(yintercept = .5, size = .15, linetype = "dashed") +
  scale_y_continuous(name="PLF", limits=c(.3, 1.05), breaks = c(.5,.75,1)) +
  ggtitle("Experiment 1") +
    stat_summary(fun.data = mean_se, fill="yellow", color = "black", shape=23, size = 1.75)

h1
```


#### Comparisons to chance

We used one-sample t tests, mu = 0.50.

```{r echo=FALSE}
t.test(e1_highlighting$Experimental_H, mu = .5, alternative = "two.sided")
t.test(e1_highlighting$Control_H, mu = .5, alternative = "two.sided")
```

```{r}
cohensD(e1_highlighting$Experimental_H, mu = .5)
cohensD(e1_highlighting$Control_H, mu = .5)
```



# Experiment 2

# Supplementary analysis

This analysis looks at the proportion of looking at the familiar object during highlighting.

Prepare the data.
```{r include=FALSE}
#Gather the columns into long format
e2_highlighting <- dataHighlighting %>%
  filter(Experiment == "Experiment 2") 
```

```{r include=FALSE}
e2_highlighting_long <- e2_highlighting %>%
  gather(key="Condition", value="PLF_H", c("Experimental_H","Control_H"))

#Convert Time as factor
e2_highlighting_long$Condition <- factor(e2_highlighting_long$Condition,
                  levels = c("Experimental_H","Control_H"),
                  labels = c("Experimental","Control"))
```


#### Descriptive statistics
Compute the summary descriptive statistics.
```{r echo=FALSE}
e2_highlighting_long %>%
  group_by(Condition) %>%
  get_summary_stats(PLF_H,type = "mean_sd")
```

#### Normality

Perform the Shapiro-Wilk test of normality with word x condition x order.

```{r echo=FALSE}
#Normality
e2_highlighting_long %>%
  group_by(Condition) %>%
  shapiro_test(PLF_H)
```

```{r echo=FALSE, warning=FALSE}
p <- gghistogram(e2_highlighting_long, x = "PLF_H",
                 ggtheme = theme_pubclean(),
                 add = "mean", rug = TRUE, bins = "8",
                 alpha = .2,
                 palette = c("#00AFBB", "#E7B800"),
                 xlab = "Difference Score") +
          facet_grid( ~ Condition, labeller = "label_both")

p + 
  font("x.text", size = 6.5) 
```

#### ANOVAs
##### Condition x order
```{r echo=FALSE, warning=FALSE}
#Run the analysis
a2horder <- aov_car(PLF_H ~ Condition*Order + Error(Id/Condition) + Order, 
                   data = e2_highlighting_long)
#Display the results
summary(a2horder)
```
#### Figure
```{r echo=FALSE}
m <- stat_summary(geom ="point", fun.y=mean, shape=18, size=4, color="blue", fill="blue", 
                  position = position_dodge(width = 0.75)) 

h2 <- ggplot(data = e2_highlighting_long, aes(x=Condition, y=PLF_H)) +
  theme_light(
  ) +
  geom_boxplot(outlier.size = -1, fill = "gray95", size = .25, width = .4) +
  geom_jitter(color="gray50",position = position_jitter(.1), size = 1.55) +
  theme(strip.text = element_text(size = 16),
                plot.title = element_text(size = 24),
                panel.grid.minor.y = element_blank(),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.x =element_text(size=20),
                axis.text.y =element_text(size=18, color="white"),
                axis.title.y=element_blank(), #element_text(size=14,face="bold"),
                axis.title.x = element_blank()) +
  geom_hline(yintercept = .5, size = .15, linetype = "dashed") +
  scale_y_continuous(name="PLF", limits=c(.3, 1.05), breaks = c(.5,.75,1)) +  
  ggtitle("Experiment 2") +
  stat_summary(fun.data = mean_se, fill="yellow", color = "black", shape=23, size = 1.75)
  #m

h2

```

#### Comparision btw highlighting conditions

```{r echo=FALSE}
wilcox.test(e2_highlighting$Control_H, e2_highlighting$Experimental_H, paired = TRUE)
```


##### Comparisons to chance

Experimental condition.
```{r echo=FALSE}
t.test(e2_highlighting$Experimental_H, mu = .5, alternative = "two.sided")
```
Control condition.
```{r}
wilcox.test(e2_highlighting$Control_H, mu = 0.5, alternative = "two.sided")
```


# Summary figures
s
```{r echo=FALSE}
fig <- ggarrange(h1, h2,
          ncol = 2, widths = c(1,1),
          #labels = c("A", "B"),
          common.legend = TRUE, legend = "bottom")

annotate_figure(fig,
                left = text_grob("PLF", color = "black", rot = 90,
                                 face = "bold", size = 24))

ggsave("plots/figure3h.png", plot = last_plot(), width = 32/1.5, height = 28/1.5, units = c("cm"))
```

